### 2014-06-04 writing/S'14 paper/quantifiers.tex
Proofed sec. 5

We evaluate the model using two experimental settings. In the simpler
setting, \textsc{all split}, we randomly sample 85\% of the data and evaluate on the
remaining 15\%. In this setting, the model is being asked to learn a
complete reasoning system for the limited language and logic presented
in the training data, but it is not being asked to generalize to test
examples that are substantially different from those it was trained
on. Crucially though, to succeed on this task, the model must be able
to recognize all of the lexical relations between the nouns, verbs,
and quantifiers and how they interact. For instance, it might see
\eqref{p1} and \eqref{p2} in training and, from that information,
determine \eqref{p3}.
%
\begin{gather}
  \text{(most turtle) swim} \natalt \text{(no turtle) move}\label{p1}
  \\
  \text{(all lizard) reptile} \natrev  \text{(some lizard) animal}\label{p2}
  \\
  \text{(most turtle) reptile} \natalt \text{(no turtle) animal}\label{p3}
\end{gather}

@@

While our primary interest is in discovering the extent to which our
models' can learn to encode the logic given an arbitrary amount of
data, we are also interested in the degree to which they can infer a
correct representation from the logic from more constrained training
data. To this end, we segment the sentence pairs according to which
quantifiers appear in each pair, and then hold out one such pair for
testing. We hypothesize that a model that can efficiently learn to
represent a logic should be able to construct an accurate
representation of each held out quantifier from the way that it
interacts with the other nine quantifiers which are not held
out. Since running this experiment requires choosing a pair of
quantifiers to hold out before training, the resource demands of
training prevent us from testing each of the 55 possible possible
pairs of quantifiers, and we choose only four pairs to test on.  Three
of these (\ii{two}/\ii{less-than-two}, \ii{not-all}/\ii{not-most}, and
\ii{all}/\ii{some}) were chosen because they determine the most
diverse set of logical relationship in our data, thereby providing the
most complex training and testing scenario possible. The fourth is a
self-pair (\ii{no}/\ii{no}), as a check to make sure the model does
perfectly on maximally easy instances.

\begin{table}[htp]
  \centering
  \begin{tabular}{ l rrr }
    \toprule
    Data & Most frequent class & TODO dim RNN (\%) & 16 dim RNTN (\%)\\
    \midrule
    \textsc{all split}	& 35.4 &	60.4&	94.4
    \\[1ex]    
    \textsc{pair two/less-than-two}	& 59.8 &	76.4 &	97.1 \\
    \textsc{pair not-all/not-most}	&0 &	   65.6  &	79.2 \\
    \textsc{pair all/some}	& 0& 60.7  &	79.5 \\
    \textsc{pair no/no}	& 30.8 &	65.8 &	100 \\
    \bottomrule
  \end{tabular}
  \caption{Quantifier experiment performance. 
    Most frequent class accuracy is measured against the most frequent class in the training data, $\natind$.}
  \label{resultstable}
\end{table}

\mynote{
The RNN model was approximately optimal with N dimensional word representations and an M dimensional comparison layer. The RNTN was approximately optimal with N and M dimensions, respectively.
% TODO: Update dimensionality
(Note: Models still running. Results might improve and this para is
likely to change.) The strong performance by the RNN on the
\textsc{pair no/no} experiment suggests that it is at least plausible
that this model is able to handle quantifiers correctly given
sufficient training data, but the sub 90\% results on most of the
training settings suggest that the data provided in these experiments
are not generally sufficient, and that the model may not be able to
learn to reason with quantifiers with high accuracy. However, the fact
that both models perform far above baseline is promising, and the
question of how much data is necessary to accurately capture
quantifier behavior in a na\"ive model remains open.

>>>>

We evaluate the model using two experimental settings. In the simpler
setting, \textsc{all split}, we randomly sample 85\% of the data and evaluate on the
remaining 15\%. In this setting, the model is being asked to learn a
complete reasoning system for the limited language and logic presented
in the training data, but it is not being asked to generalize to test
examples that are substantially different from those it was trained
on. Crucially though, to succeed on this task, the model must be able
to recognize all of the lexical relations between the nouns, verbs,
and quantifiers and how they interact. For instance, it might see
\eqref{p1} and \eqref{p2} in training and, from that information,
determine \eqref{p3}.
%
\begin{gather}
  \text{(most turtle) swim} \natalt \text{(no turtle) move}\label{p1}
  \\
  \text{(all lizard) reptile} \natfor  \text{(some lizard) animal}\label{p2}
  \\
  \text{(most turtle) reptile} \natalt \text{(no turtle) animal}\label{p3}
\end{gather}

@@

While our primary interest is in discovering the extent to which our
models' can learn to encode the logic given an arbitrary amount of
data, we are also interested in the degree to which they can infer a
correct representation from the logic from more constrained training
data. To this end, we segment the sentence pairs according to which
quantifiers appear in each pair, and then hold out one such pair for
testing. We hypothesize that a model that can efficiently learn to
represent a logic should be able to construct an accurate
representation of each held out quantifier from the way that it
interacts with the other nine quantifiers which are not held
out. Since running this experiment requires choosing a pair of
quantifiers to hold out before training, the resource demands of
training prevent us from testing each of the 55 possible possible
pairs of quantifiers, and we choose only four pairs to test on.  Three
of these (\ii{two}/\ii{less-than-two}, \ii{not-all}/\ii{not-most}, and
\ii{all}/\ii{some}) were chosen because they determine the most
diverse set of logical relationship in our data, thereby providing the
most complex training and testing scenario possible. The fourth is a
self-pair (\ii{no}/\ii{no}), meant to test that the model correctly
handles equality.

% Further explanation for motivation for no/no?

\begin{table}[htp]
  \centering
  \begin{tabular}{ l rrr }
    \toprule
    Data & Most frequent class & TODO dim RNN (\%) & 16 dim RNTN (\%)\\
    \midrule
    \textsc{all split}	& 35.4 &	60.4&	\textbf{94.4}
    \\[1ex]    
    \textsc{pair two/less-than-two}	& 59.8 &	76.4 &	\textbf{97.1} \\
    \textsc{pair not-all/not-most}	&0 &	   65.6  &	\textbf{79.2} \\
    \textsc{pair all/some}	& 0& 60.7  &	\textbf{79.5} \\
    \textsc{pair no/no}	& 30.8 &	65.8 &	\textbf{100} \\
    \bottomrule
  \end{tabular}
  \caption{Quantifier experiment performance. 
    The most frequent class baseline accuracy reflects the most frequent class in the training data, $\natind$.}
  \label{resultstable}
\end{table}

\mynote{
The RNN model was approximately optimal with N dimensional word representations and an M dimensional comparison layer. The RNTN was approximately optimal with N and M dimensions, respectively.
% TODO: Update dimensionality
(Note: Models still running. Results might improve and this para is
likely to change.) The perfect performance by the RNTN on the
\textsc{pair no/no} experiment and its strong performance on
\textsc{pair two/less-than-two} suggests that it is at least plausible
that this model is able to handle quantifiers correctly given
sufficient training data, but the sub 90\% results on two of the
training settings suggest that the model may not be able to
generalize from data this impoverished in general. However, the fact
that both models perform far above baseline is promising, and the
question of how much data is necessary to accurately capture
quantifier behavior in a na\"ive model remains open.
